\texttt{\df} -- \\ modifying drafted figures\footnote{ For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure} Comments and criticisms are welcome.}

### 2017-05-07 draftfigure-preamble.tex
documentation

\usepackage[%
%  flushmargin, %
%  marginal,
  ragged,%
  hang, %
  bottom%
]{footmisc}

@@

\newtcblisting[
auto counter,
]{code}{%
    listing only,
    breakable,
    top=0.2pt,
    bottom=0.2pt,
    colback=codegreen!10,
    colframe=codegreen,
    left=5pt,
    right=5pt,
      sharp corners,
    boxrule=0pt,
    bottomrule=0pt,
    toprule=0pt,
    enhanced jigsaw,
    listing options={%style=tcblatex,
%        numbers=left,
        numberstyle=\tiny\color{codeblue},
        moredelim={[is][keywordstyle]{@@}{@@}},
        basicstyle=\small\ttfamily,
        breaklines=true,
        breakautoindent=false,
        breakindent=0pt,
        escapeinside={{*@}{@*}},
    },%
    lefttitle=0pt,
    coltitle=codeblue,
    colbacktitle=codegreen!10,
%    fonttitle=\bfseries\footnotesize,
%    title={Example \thetcbcounter:  #2}, 
%   #1,%  
%    borderline north={1pt}{14.4pt}{codegreen,dashed},
}

@@

\tcbset{examplebox/.style={%
  boxrule=0pt,
  bottomrule=2pt,
  toprule=2pt,
 colframe=codeblue,
  colback=codegreen!10,
   coltitle=codegreen!10,%  coltitle=codeblue,
  bicolor,
      sharp corners,
 fontupper=\small\ttfamily,
  colbacklower=codeblue!10,
  fonttitle=\sffamily\bfseries,
  }}

>>>>

@@

\newtcblisting[
auto counter,
]{code}{%
  before skip=2em,after skip=2em,
    listing only,
    breakable,
    top=0.2pt,
    bottom=0.2pt,
    colback=codegreen!10,
    colframe=codegreen,
    left=5pt,
    right=5pt,
      sharp corners,
    boxrule=0pt,
    bottomrule=0pt,
    toprule=0pt,
    enhanced jigsaw,
    listing options={%style=tcblatex,
%        numbers=left,
        numberstyle=\tiny\color{codeblue},
        moredelim={[is][keywordstyle]{@@}{@@}},
        basicstyle=\small\ttfamily,
        breaklines=true,
        breakautoindent=false,
        breakindent=0pt,
        escapeinside={{*@}{@*}},
    },%
    lefttitle=0pt,
    coltitle=codeblue,
    colbacktitle=codegreen!10,
%    fonttitle=\bfseries\footnotesize,
%    title={Example \thetcbcounter:  #2}, 
%   #1,%  
%    borderline north={1pt}{14.4pt}{codegreen,dashed},
}

@@

\tcbset{examplebox/.style={%
  before skip=2em,after skip=2em,
  boxrule=0pt,
  bottomrule=2pt,
  toprule=2pt,
 colframe=codeblue,
  colback=codegreen!10,
   coltitle=codegreen!10,%  coltitle=codeblue,
  bicolor,
      sharp corners,
 fontupper=\small\ttfamily,
  colbacklower=codeblue!10,
  fonttitle=\sffamily\bfseries,
  }}

### 2017-05-07 draftfigure.tex
documentation

\input{draftfigure-preamble.tex}
\newcommand\df{draftfigure\xspace}
\newcommand\dfstring{|draftfigure|\xspace}
\setkeys{Gin}{width=.3\linewidth}

\begin{document}
\title{\texttt{\df} -- \\ modifying drafted figures\footnote{%
For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure}: 
Comments and criticisms are welcome.}}
\author{Lukas C. Bossert\\{\small \href{mailto:lukas@digitales-altertum.de}{lukas@digitales-altertum.de}}}
\date{Version: \dfdate{} (\dfversion)} 
\maketitle

@@

\section{Installation}
\dfstring is part of the distributions MiK\TeX \footnote{Website: \url{http://www.miktex.org}.} 
and \TeX Live\footnote{Website: \url{http://www.tug.org/texlive}.}~-- thus, you
can easily install it using the respective package manager. 
If you would like to
install \dfstring manually, do the following:
Download the folder \dfstring with all relevant files from the CTAN-server\footnote{\url{https://www.ctan.org/pkg/\df}} and copy the content of the |zip|-file to the \texttt{\$LOCALTEXMF} directory of
 your system.\footnote{If you don't know what that is, have a look at
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=tds} or 
\url{http://mirror.ctan.org/tds/tds.html}.} 
Refresh your filename database.\footnote{ 
Here is some additional information from the UK \TeX\ FAQ:
\begin{itemize}[nosep,after=\vspace{-\baselineskip} ]
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=install-where}{%
    Where to install packages}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{%
    Installing files \enquote{where \LaTeX /TeX\ can find them}}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=privinst}{%
    \enquote{Private} installations of files}
\end{itemize}
}
%%introduction from biblatex-dw copied and applied. might to be rewritten.

@@

If you do not like the outcome with the filename and its path written with |\ttfamily| then use \dfstring.
\clearpage

@@

\begin{code}
\usepackage[%
  *@\meta{further options}@*
  ]{draftfigure}
\end{code}
Without any further  Now you will now get white boxes instead of the images.
\begin{examplebox}
\begin{figure}[H]\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage

\section{Options}

\subsection{Preamble}
\subsubsection{style}
\subsubsection{size}
\subsubsection{position}
\subsubsection{allfiguresdraft}
\subsubsection{content}
\subsubsection{filename}
\subsubsection{noframe}

\subsection{Individually possible}

@@

\subsubsection{style}
\subsubsection{size}
\subsubsection{position}
\subsubsection{content}
\subsubsection{filename}
\clearpage

>>>>

\input{draftfigure-preamble.tex}
\newcommand\df{draftfigure\xspace}
\newcommand\dfstring{|draftfigure|\xspace}
\setkeys{Gin}{width=.4\linewidth}

\begin{document}
\title{\texttt{\df} -- \\ modifying drafted figures\footnote{%
For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure}
Comments and criticisms are welcome.}}
\author{Lukas C. Bossert\\{\small \href{mailto:lukas@digitales-altertum.de}{lukas@digitales-altertum.de}}}
\date{Version: \dfdate{} (\dfversion)} 
\maketitle

@@

\section{Installation}
\dfstring is part of the distributions MiK\TeX \footnote{Website: \url{http://www.miktex.org}.} 
and \TeX Live\footnote{Website: \url{http://www.tug.org/texlive}.}~-- thus, you
can easily install it using the respective package manager. 
If you would like to
install \dfstring manually, do the following:
Download the folder \dfstring with all relevant files from the CTAN-server\footnote{\url{https://www.ctan.org/pkg/\df}} and copy the content of the |zip|-file to the \texttt{\$LOCALTEXMF} directory of
 your system.\footnote{If you don't know what that is, have a look at
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=tds} or 
\url{http://mirror.ctan.org/tds/tds.html}.} 
Refresh your filename database.

Here is some additional information from the UK \TeX\ FAQ:
\begin{itemize}[nosep,after=\vspace{-\baselineskip} ]
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=install-where}{%
    Where to install packages}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{%
    Installing files \enquote{where \LaTeX /TeX\ can find them}}
  \item \href{%
    http://www.tex.ac.uk/cgi-bin/texfaq2html?label=privinst}{%
    \enquote{Private} installations of files}
\end{itemize}

%%introduction from biblatex-dw copied and applied. might to be rewritten.

@@

If you do not like the outcome with the filename and its path written with |\ttfamily| then use this package \dfstring to modify the outcome.
\clearpage

@@

\begin{code}
\usepackage[%
  *@\meta{further options}@*
  ]{draftfigure}
\end{code}
Without any further options you will now get white boxes instead of the images.
\begin{examplebox}
\begin{figure}[H]\setkeys{Gin}{draft=true}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
The size of the boxes are identical to the size of the images which you can define optionally with |[width=.3\linewidth]|
\clearpage

\section{Options}
If you like the plain white boxes you don’t need to do anything else. But if you like to change that use one or more of the following options.

So let’s see some action.
\subsection{Preamble}
The following options are set in the preamble and considered globally for all figures.
\subsubsection{content}
\DescribeMacro{content}
With this option you can set an individual text which will be displayed in the white box.
\begin{code}
\usepackage[%
  content = {This figure is omitted due to missing copyrights.},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{draftfigure}{content = {This figure is omitted due to missing copyrights.}}
	\setkeys{Gin}{draft=true}
  \centering
  \includegraphics[width=.4\linewidth]{example-image-a}
  \caption{A}
  \includegraphics[width=.4\linewidth]{example-image-b}
  \caption{B}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{filename}
\DescribeMacro{filename}
Activating this option with |true| the filename will be displayed in the white box.
If you also have defined some text for |content| the filename will appear one line below of |content|.
\begin{code}
\usepackage[%
  filename,%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
And with some text in |content| it will look like this:
\begin{code}
\usepackage[%
  filename,%
  content={no image available}
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{filename,
	content={no image available}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  \includegraphics{example-image-c}
  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{style}
\DescribeMacro{style} This defines the font style of the text of |content| or |filename|. 
You can chose one of the following styles: 
\begin{itemize}
	\item[sf] |\sffamily|
	\item[tt] |\ttfamily|
	\item[rm] |\rmfamily|
	\item[normal] |\normalfont|
	\item[bf] |\bfseries|
	\item[it] |\itshape|
	\item[sc] |\scshape|
\end{itemize}
Default is |sf|.
\begin{code}
\usepackage[%
  content={hidden image},
  style = {bf},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{style={bf},content={hidden image}}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  \includegraphics{example-image-b}
  \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}
\clearpage
\subsubsection{size}
\DescribeMacro{size}
You can also define the text size of |content| with predefined values: 
\begin{itemize}
	\item[tiny] |\tiny|
	\item[scriptsize] |\scriptsize|
	\item[small] |\small|
	\item[footnotesize] |\footnotesize|
	\item[normal] |\normalsize|
	\item[large] |\large|
	\item[Large] |\Large|
	\item[LARGE] |\LARGE|
	\item[huge] |\huge|
\end{itemize} 
Default is |small|.
\begin{code}
\usepackage[%
  content={text instead of an image},
  size = {huge},%
  ]{draftfigure}
\end{code}
\begin{examplebox}
\begin{figure}[H]
	\setkeys{Gin}{draft=true}
	\setkeys{draftfigure}{
  content={text instead of an image},
  size = {huge},%
	}
  \centering
  \includegraphics{example-image-a}
  \caption{A}
  % \includegraphics{example-image-b}
  % \caption{B}
  % \includegraphics{example-image-c}
 %  \caption{C}
\end{figure}
\end{examplebox}

\subsubsection{position}
\DescribeMacro{position}

\subsubsection{allfiguresdraft}
\DescribeMacro{allfiguresdraft}

\subsubsection{noframe}
\DescribeMacro{noframe}

\clearpage
\subsection{Individually possible}

@@

\subsubsection{style}
\DescribeMacro{style}

\subsubsection{size}
\DescribeMacro{size}

\subsubsection{position}
\DescribeMacro{position}

\subsubsection{content}
\DescribeMacro{content}

\subsubsection{filename}
\DescribeMacro{filename}

\clearpage
